An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-09-29 paper.tex
Update intro to §5.2

As we showed in Section \ref{sec:org-dyn:participants}, protocol
standardisation is an inherently social process with most day-to-day work
happening on public mailing lists, aided by meetings, video conference
calls, and open document and code repositories.  We are specifically
interested in better understanding how influence is distributed across
stakeholders and how it might affect the standardisation process.  This is
of critical societal importance: the IETF has a major impact on global
Internet technologies, and understanding the social processes involved
would give us insight into not only the driving forces behind
standardisation, but also its resilience to the loss of major participants.
In this section we consider the following research questions: 
\begin{enumerate}
  \item How centralised is the active IETF community, and to what extent
    is it reliant on a small core of participants? 
  \item How do the most influential participants behave? 
  \item How does influence (determined by mailing list participation)
    relate to wider impacts throughout the IETF?
  \item Does the organisational affiliation of participants also
    influence the innovation (adoption of new work) within IETF?
\end{enumerate}

>>>>

As we showed in Section \ref{sec:org-dyn:participants}, protocol
standardisation is an inherently social process with most day-to-day work
happening on public mailing lists.  We are specifically
interested in better understanding how influence is distributed across
stakeholders and how it might affect the standardisation process.  This is
of critical societal importance: the IETF has a major impact on global
Internet technologies, and understanding the social processes involved
would give us insight into not only the driving forces behind
standardisation, but also its resilience to the loss of major participants.
In this section we consider the following research questions: 
\begin{enumerate}
  \item How centralised is the active IETF community, and to what extent
    is it reliant on a small core of participants? 
  \item How do the most influential participants behave? 
  \item How does influence (determined by mailing list participation)
    relate to wider impacts throughout the IETF?
  \item Does the organisational affiliation of participants also
    influence the innovation (adoption of new work) within IETF?
\end{enumerate}
